---
title: "Maverik Project Exploratory Data Analysis"
author: "Jade Gosar"
output: html_document
date: "2023-10-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(lubridate)
library(tidyverse)
library(zoo)
library(ggplot2)
library(melt)
library(reshape2)
library(corrplot)
library(knitr)
library(formattable)
library(kableExtra)
library(gridExtra)
```


```{r}
qualitative_data <- read_csv("qualitative_data_msba.csv")

time_series_data <- read_csv("time_series_data_msba.csv")
```

## Numbered Day Analysis
This approach indexes each observation by the number of days that have passed since the respective store opened. In this approach, the first day that the store is open is given a value of "0" in the created column called "Days_Since_Open". From this point, every day is given a value that is calculated based on the number of days that have passed since the store opened through its first year.

```{r numeric_day_analysis}
#Creates a df using read_csv that handles dates differently
time_series_data <- read_csv("time_series_data_msba.csv", 
    col_types = cols(capital_projects.soft_opening_date = col_date(format = "%m/%d/%Y"), 
        calendar.calendar_day_date = col_date(format = "%m/%d/%Y")))

# Create column that shows the number of days the store has been open
ts_w_days <- time_series_data %>%
  mutate(Days_Since_Open = as.numeric(calendar.calendar_day_date - capital_projects.soft_opening_date)) %>%
  rename("row_id" = "...1") %>%
  arrange(site_id_msba, calendar.calendar_day_date)


# Define the major holidays data frame
major_holidays <- data.frame(
  calendar.calendar_day_date = as.Date(c(
    "2021-01-01", "2021-01-18", "2021-04-04",
    "2021-05-31", "2021-07-04", "2021-09-06", "2021-10-11", "2021-11-11", "2021-11-25", "2021-12-24",
    "2021-12-25", "2021-12-31", "2022-01-01", "2022-01-17",
    "2022-04-17", "2022-05-30", "2022-07-04", "2022-09-05",
    "2022-10-10", "2022-11-11", "2022-11-24",
    "2022-12-24", "2022-12-25", "2022-12-31"
  )),
  Major_Holiday = c(
    "New Year's Day", "Martin Luther King Jr. Day", "Easter Sunday",
    "Memorial Day", "Independence Day", "Labor Day", "Columbus Day",
    "Veterans Day", "Thanksgiving Day", "Christmas Eve", "Christmas Day",
    "New Year's Eve", "New Year's Day", "Martin Luther King Jr. Day",
    "Easter Sunday", "Memorial Day", "Independence Day", "Labor Day",
    "Columbus Day", "Veterans Day", "Thanksgiving Day", "Christmas Eve",
    "Christmas Day", "New Year's Eve"
  )
)

# Merge the original data frame with the major holidays data frame
ts_w_holidays <- ts_w_days %>%
  left_join(major_holidays, by = c("calendar.calendar_day_date" = "calendar.calendar_day_date"))

# Make indicator for whether the day fell on a holiday given by Maverik
ts_all_holidays <- ts_w_holidays %>%
  mutate(General_Holiday = ifelse(calendar_information.holiday == "NONE", 0, 1))
```

## Sales variaton by day of week
There appears to be some clear trends by day of week that span the different target variables. For example, average sales fall on Sunday for each of the individual target variables. 

```{r}
#Creates a day of week summary dataframe 
dow_summary <- ts_all_holidays %>%
  group_by(calendar.day_of_week) %>%
  summarize(Avg_inside_sales = mean(daily_yoy_ndt.total_inside_sales),
            Avg_food_service = mean(daily_yoy_ndt.total_food_service),
            Avg_diesel_sales = mean(diesel),
            Avg_unleaded_sales = mean(unleaded))

# Create the table using kable for better display in html
html_table <- knitr::kable(dow_summary, format = "html")

# Apply kable_styling to adjust column width
day_of_week_summary_table <- kable_styling(html_table, full_width = TRUE)  # Set full_width to TRUE if you want the table to occupy the full width of the page

# Print the day of the week summary table
day_of_week_summary_table
```

```{r, out.width='100%', out.height='100%'}
# Reshape data from wide to long format
data_long <- dow_summary %>%
  pivot_longer(cols = starts_with("Avg_"), names_to = "Sales_Type", values_to = "Average_Sales")

# Order of the days of the week
day_order <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")

# Apply the order to the factor levels
data_long$calendar.day_of_week <- factor(data_long$calendar.day_of_week, levels = day_order)

# Create a line chart with ordered days
line_chart_ordered <- ggplot(data_long, aes(x = calendar.day_of_week, y = Average_Sales, color = Sales_Type, group = Sales_Type)) +
  geom_line(size = 2) +
  labs(title = "Trends in Sales Categories over Days of Week",
       x = "Day of the Week", y = "Average Sales", color = "Sales Type") +
  theme_minimal() +
  theme(legend.position = "top")

# Print the plot
print(line_chart_ordered)
```

The following boxplot for average sales by day of week indicates a slight uptick in sales for Thursday and Friday. There appear to be outliers for each of the estimates that might be partially explained by holiday travel. 

```{r, out.width='100%', out.height='100%'}
# Reorder the factor levels of calendar.day_of_week
ts_all_holidays$calendar.day_of_week <- factor(ts_all_holidays$calendar.day_of_week, levels = day_order)

# Create the boxplot with the ordered days of the week
day_of_week_bp <- ggplot(ts_all_holidays,
  aes(x = calendar.day_of_week, y = unleaded, color = calendar.day_of_week)) +
  geom_boxplot(fill = "white") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  labs(title = "Unleaded Sales tend to be the highest on Fridays", x = "Day of Week", y = "Unleaded Sales") +
  guides(color = FALSE)

# Prints the day of week boxplot
day_of_week_bp
```

```{r}
# Create line graph of all stores sales over time
ggplot(ts_all_holidays, aes(x = Days_Since_Open, y = daily_yoy_ndt.total_inside_sales, group = site_id_msba, color = factor(site_id_msba))) +
  geom_line() +
  labs(title = "Daily YOY Total Inside Sales",
       x = "Days Since Open",
       y = "Total Inside Sales",
       color = "Store ID") +
  theme_minimal()
```

## Sales categories variaton over time
To better understand trends of sales for the main categories over the same window of time (from the day the store opened through the first year), we selected four stores that have varying qualitative variables associated with them. Inside and food sales are fairly consistent across the stores selected but there is some variation in unleaded sales and a clear distinction in diesel sales of store 21980 compared to the others. It is more difficult to distinguish the differences in unleaded sales; however, store 22785 seems to experiencing the same seasonal trend but on a different timeline. This finding is how we began to question if we should create a feature that shows what season the store opened in which would allow us to address these potential differences in the modeling process.

```{r, out.width='100%', out.height='100%'}
# Choose stores to highlight their trends over time
selected_stores <- c(21980, 23240, 24150, 22785)
#selected_stores <- c(21560, 22015, 22085, 22120)
#selected_stores <- c(22260, 22330, 22400, 22505)
#selected_stores <- c(22540, 22575, 22645, 22680)
#selected_stores <- c(22715, 22750, 22820, 22855)
#selected_stores <- c(22890, 22925, 23065, 23135)
#selected_stores <- c(23345, 23380, 23415, 23450)
#selected_stores <- c(23485, 23555, 23660, 23730)
#selected_stores <- c(23765, 23835, 23905, 24220, 24535)

# Filter the data to include only the selected stores
stores_of_interest <- ts_all_holidays[ts_all_holidays$site_id_msba %in% selected_stores, ]

#creates a subset of stores of interest
soi_long <- stores_of_interest %>%
  dplyr::select("Days_Since_Open", "site_id_msba", "daily_yoy_ndt.total_inside_sales", "daily_yoy_ndt.total_food_service","diesel","unleaded") %>%
  rename("inside_sales" = "daily_yoy_ndt.total_inside_sales",
         "food_sales" = "daily_yoy_ndt.total_food_service")

#creates a long form of the previous subset
soi_long <- melt(soi_long, id.vars = c("Days_Since_Open","site_id_msba"), variable.name = "product_type", value.name = "average_sales")

#generates a facet plot of the select stores
ggplot(soi_long, aes(x=Days_Since_Open, y=average_sales, group = site_id_msba, color=factor(site_id_msba))) +
  geom_line(size = 1) + facet_wrap(~product_type) + 
  labs(title = "Daily Sales for Selected Stores",
       x = "Number of Days Open",
       y = "Total Sales",
       color = "Store ID") +
  theme_minimal()

```

```{r stores}
#Creates a dataframe with a store-level focus
stores_df <- ts_all_holidays %>%
  dplyr::select("site_id_msba", 
         "diesel", 
         "unleaded", 
         "daily_yoy_ndt.total_inside_sales",
         "daily_yoy_ndt.total_food_service") %>%
  rename("site_id" = "site_id_msba",
         'inside_sales' = 'daily_yoy_ndt.total_inside_sales',
         'food_sales' = 'daily_yoy_ndt.total_food_service'
         )

#Average values for stores
stores_tibble <- stores_df %>%
  group_by(site_id) %>%
  summarize(Avg_Gas= mean(unleaded),
            Avg_Diesel = mean(diesel),
            Avg_Store_Sales = mean(inside_sales),
            Avg_Food_Sales = mean(food_sales))

# Only display the top 10 rows in html output
top_10_rows <- head(stores_tibble, 10)

# Create the table using kable for better display in html
stores_table <- knitr::kable(top_10_rows, format = "html")

# Apply kable_styling to adjust column width
store_averages_table <- kable_styling(stores_table, full_width = TRUE)  # Set full_width to TRUE if you want the table to occupy the full width of the page

# Print the store_averages_table table
store_averages_table
```

## Differences in Holidays and Non-holidays
We think that holidays could be an important consideration to make in the modeling process as days and weekends associated with them could be impactful on sales projections. For this reason we wanted to look at the holidays given by Maverik, which we labeled as "general holidays", compared to non-holidays as well as holidays we deemed as "major holidays", meaning customers generally get the day or days surrounding it off from work or school. The table below shows general holidays tend to have lower sales in all categories when it comes to average and maximum sales compared to regular days; however, there does not appear to be any significant differences that should be investigated further.

```{r}
ts_with_holidays <- ts_all_holidays %>%
  mutate(major_holiday_indicator = ifelse(Major_Holiday == "NA", 0, 1))

holiday_table <- ts_with_holidays %>%
  mutate(General_Holiday = ifelse(General_Holiday == 0, "Not a holiday", "General Holiday")) %>%
  group_by(General_Holiday) %>%
  summarize(`Maximum Unleaded Sales` = max(unleaded),
            `Minimum Unleaded Sales` = min(unleaded),
            `Average Unleaded Sales` = mean(unleaded),
            `Maximum Diesel Sales` = max(diesel),
            `Minimum Diesel Sales` = min(diesel),
            `Average Diesel Sales` = mean(diesel),
            `Maximum Inside Sales` = max(daily_yoy_ndt.total_inside_sales),
            `Average Inside Sales` = mean(daily_yoy_ndt.total_inside_sales),
            `Maximum Food Sales` = max(daily_yoy_ndt.total_food_service),
            `Average Food Sales` = mean(daily_yoy_ndt.total_food_service))

# Create the table using kable for better display in html
holidays <- knitr::kable(holiday_table, format = "html")

# Apply kable_styling to adjust column width
holiday_summary_table <- kable_styling(holidays, full_width = TRUE)  # Set full_width to TRUE if you want the table to occupy the full width of the page

# Print the holiday summary table
holiday_summary_table
```

To better capture how holidays may impact sales at Maverik, we decided to narrow the scope by distinguishing major holidays from general holidays. The below table shows larger differences when distinguishing major holidays from the rest of the business days, meaning that sales, on average, tend to be lower across all categories when it is a major holiday compared against general holidays and regular business days.  

```{r}
major_holiday_table <- ts_with_holidays %>%
  mutate(major_holiday_indicator = ifelse(major_holiday_indicator == 1, "Major Holiday", "")) %>%
  group_by(major_holiday_indicator) %>%
  summarize(`Maximum Unleaded Sales` = max(unleaded),
            `Minimum Unleaded Sales` = min(unleaded),
            `Average Unleaded Sales` = mean(unleaded),
            `Maximum Diesel Sales` = max(diesel),
            `Minimum Diesel Sales` = min(diesel),
            `Average Diesel Sales` = mean(diesel),
            `Maximum Inside Sales` = max(daily_yoy_ndt.total_inside_sales),
            `Average Inside Sales` = mean(daily_yoy_ndt.total_inside_sales),
            `Maximum Food Sales` = max(daily_yoy_ndt.total_food_service),
            `Average Food Sales` = mean(daily_yoy_ndt.total_food_service)) %>%
  rename("Type of Day" = major_holiday_indicator)

# Replace NA with "Normal Business Day" in the table
major_holiday_table$`Type of Day` <- ifelse(is.na(major_holiday_table$`Type of Day`), "Normal Business Day", major_holiday_table$`Type of Day`)

# Create the table using kable for better display in html
major_holidays <- knitr::kable(major_holiday_table, format = "html")

# Apply kable_styling to adjust column width
major_holidays_summary_table <- kable_styling(major_holidays, full_width = TRUE)  # Set full_width to TRUE if you want the table to occupy the full width of the page

# Print the major holiday summary table
major_holidays_summary_table
```

```{r}
# Create the density plot for Food Service Sales
food_service_plot <- ggplot(ts_with_holidays, aes(x = daily_yoy_ndt.total_food_service, fill = as.factor(`major_holiday_indicator`))) +
  geom_density(alpha = 0.6) +
  labs(title = "Food Service Sales Distributions", x = "Sales", fill = "Type of Day") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  scale_fill_manual(values = c("#CC0000", "#C1CDCD"), 
                    labels = c("Major Holiday", "Not a holiday"))

# Create the density plot for Inside Sales
inside_sales_plot <- ggplot(ts_with_holidays, aes(x = daily_yoy_ndt.total_inside_sales, fill = as.factor(`major_holiday_indicator`))) +
  geom_density(alpha = 0.6) +
  labs(title = "Inside Sales Distributions", x = "Sales", fill = "Type of Day") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  scale_fill_manual(values = c("#CC0000", "#C1CDCD"), 
                    labels = c("Major Holiday", "Not a holiday"))

# Create the density plot for Diesel Gallons Sold
diesel_gallons <- ggplot(ts_with_holidays, aes(x = diesel, fill = as.factor(`major_holiday_indicator`))) +
  geom_density(alpha = 0.6) +
  labs(title = "Diesel Gallons Sold Distributions", x = "Gallons", fill = "Type of Day") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  scale_fill_manual(values = c("#CC0000", "#C1CDCD"), 
                    labels = c("Major Holiday", "Not a holiday"))

# Create the density plot for Unleaded Gallons Sold
unleaded_gallons <- ggplot(ts_with_holidays, aes(x = unleaded, fill = as.factor(`major_holiday_indicator`))) +
  geom_density(alpha = 0.6) +
  labs(title = "Unleaded Gallons Sold Distributions", x = "Gallons", fill = "Type of Day") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  scale_fill_manual(values = c("#CC0000", "#C1CDCD"), 
                    labels = c("Major Holiday", "Not a holiday"))

# Display all plots in one visualization
grid.arrange(food_service_plot, inside_sales_plot, diesel_gallons, unleaded_gallons, ncol = 2)

```

The above visualization confirms that major holidays may negatively affect business at Maverik, at least on the actual day of the holiday. We plan to explore this relationship further in the modeling process through feature engineering that will allow us to see if the days surrounding these holidays have an impact that lessens or exacerbates the impact holidays have on the business.

```{r}
result <- ts_all_holidays %>%
  group_by(site_id_msba) %>%
  summarise(food_sales = sum(daily_yoy_ndt.total_food_service, na.rm = TRUE),
            inside_sales = sum(daily_yoy_ndt.total_inside_sales, na.rm = TRUE),
            diesel_sales = sum(diesel, na.rm = TRUE),
            unleaded_sales = sum(unleaded, na.rm = TRUE)) %>%
  ungroup() %>%
  arrange(desc(food_sales))

most_food_sales <- result$site_id_msba[1:5]

# Filter the data to include only the selected stores
stores_of_interest <- ts_all_holidays[ts_all_holidays$site_id_msba %in% most_food_sales, ]

#creates a subset of stores of interest
soi_long <- stores_of_interest %>%
  dplyr::select("Days_Since_Open", "site_id_msba", "daily_yoy_ndt.total_inside_sales", "daily_yoy_ndt.total_food_service","diesel","unleaded") %>%
  rename("inside_sales" = "daily_yoy_ndt.total_inside_sales",
         "food_sales" = "daily_yoy_ndt.total_food_service")

#creates a long form of the previous subset
soi_long <- melt(soi_long, id.vars = c("Days_Since_Open","site_id_msba"), variable.name = "product_type", value.name = "average_sales")

#generates a facet plot of the select stores
ggplot(soi_long, aes(x=Days_Since_Open, y=average_sales, group = site_id_msba, color=factor(site_id_msba))) +
  geom_line(size = 1) + facet_wrap(~product_type) + 
  labs(title = "Daily Sales for Stores with highest Annual Food Sales",
       x = "Number of Days Open",
       y = "Total Sales",
       color = "Store ID") +
  theme_minimal()
```

```{r}
result2 <- result %>%
  arrange(desc(inside_sales))

most_inside_sales <- result2$site_id_msba[1:5]

# Filter the data to include only the selected stores
stores_of_interest <- ts_all_holidays[ts_all_holidays$site_id_msba %in% most_inside_sales, ]

#creates a subset of stores of interest
soi_long <- stores_of_interest %>%
  dplyr::select("Days_Since_Open", "site_id_msba", "daily_yoy_ndt.total_inside_sales", "daily_yoy_ndt.total_food_service","diesel","unleaded") %>%
  rename("inside_sales" = "daily_yoy_ndt.total_inside_sales",
         "food_sales" = "daily_yoy_ndt.total_food_service")

#creates a long form of the previous subset
soi_long <- melt(soi_long, id.vars = c("Days_Since_Open","site_id_msba"), variable.name = "product_type", value.name = "average_sales")

#generates a facet plot of the select stores
ggplot(soi_long, aes(x=Days_Since_Open, y=average_sales, group = site_id_msba, color=factor(site_id_msba))) +
  geom_line(size = 1) + facet_wrap(~product_type) + 
  labs(title = "Daily Sales for Stores with highest Annual Inside Sales",
       y = "Total Sales",
       color = "Store ID") +
  theme_minimal()
```

```{r}
result3 <- result %>%
  arrange(desc(diesel_sales))

most_diesel_sales <- result3$site_id_msba[1:5]

# Filter the data to include only the selected stores
stores_of_interest <- ts_all_holidays[ts_all_holidays$site_id_msba %in% most_diesel_sales, ]

#creates a subset of stores of interest
soi_long <- stores_of_interest %>%
  dplyr::select(Days_Since_Open, site_id_msba, `daily_yoy_ndt.total_inside_sales`, `daily_yoy_ndt.total_food_service`, diesel, unleaded) %>%
  dplyr::rename("inside_sales" = "daily_yoy_ndt.total_inside_sales",
         "food_sales" = "daily_yoy_ndt.total_food_service")

#creates a long form of the previous subset
soi_long <- melt(soi_long, id.vars = c("Days_Since_Open","site_id_msba"), variable.name = "product_type", value.name = "average_sales")

# Define a specific store ID to be represented in red
target_store <- "21980"

# Create a column in soi_long to differentiate the colors
soi_long$color <- ifelse(soi_long$site_id_msba == target_store, "Target", "Other")

#generates a facet plot of the select stores
ggplot(soi_long, aes(x=Days_Since_Open, y=average_sales, group = site_id_msba, color=factor(site_id_msba))) +
  geom_line(size = 1) + facet_wrap(~product_type) + 
  labs(title = "Daily Sales for Stores with highest Annual Diesel Sales",
       x = "Number of Days Open",
       y = "Total Sales",
       color = "Store ID") +
  theme_minimal()

# Manually set colors in ggplot
ggplot(soi_long, aes(x = Days_Since_Open, y = average_sales, group = site_id_msba, color = color)) +
  geom_line(size = 1) +
  scale_color_manual(values = c("Target" = "firebrick2", "Other" = "gray48"),
                     labels = c("Top Stores in Annual Diesel Sales", "Store 21980")) +
  facet_wrap(~product_type) + 
  labs(title = "Daily Sales for Stores with Highest Annual Diesel Sales",
       x = "Number of Days Open",
       y = "Total Sales",
       color = "Store ID") +
  theme_minimal() +
  theme(axis.text = element_text(size = 12, color = "black"),
        axis.title = element_text(size = 14),
        title = element_text(size = 18),
        legend.text = element_text(size = 14), # Adjust legend text size
        legend.title = element_text(size = 17),
        strip.text = element_text(size = 16))
```

```{r}
result4 <- result %>%
  arrange(desc(unleaded_sales))

most_unleaded_sales <- result4$site_id_msba[1:5]

# Filter the data to include only the selected stores
stores_of_interest <- ts_all_holidays[ts_all_holidays$site_id_msba %in% most_unleaded_sales, ]

#creates a subset of stores of interest
soi_long <- stores_of_interest %>%
  select("Days_Since_Open", "site_id_msba", "daily_yoy_ndt.total_inside_sales", "daily_yoy_ndt.total_food_service","diesel","unleaded") %>%
  rename("inside_sales" = "daily_yoy_ndt.total_inside_sales",
         "food_sales" = "daily_yoy_ndt.total_food_service")

#creates a long form of the previous subset
soi_long <- melt(soi_long, id.vars = c("Days_Since_Open","site_id_msba"), variable.name = "product_type", value.name = "average_sales")

#generates a facet plot of the select stores
ggplot(soi_long, aes(x=Days_Since_Open, y=average_sales, group = site_id_msba, color=factor(site_id_msba))) +
  geom_line(size = 1) + facet_wrap(~product_type) + 
  labs(title = "Daily Sales for  Stores with highest Annual Unleaded Sales",
       x = "Number of Days Open",
       y = "Total Sales",
       color = "Store ID") +
  theme_minimal()
```

```{r}
#imports a few key variables from qualitative data set
important_qual <- qual_data %>%
  select(
    "site_id_msba",
    "square_feet",
    "parking_spaces",
    "lottery",
    "bonfire_grill",
    "pizza",
    "ethanol_free",
    "hi_flow_lanes",
    "rv_lanes",
    "def",
    "rv_dumps",
    "x1_mile_pop",
    "x1_mile_emp",
    "x1_mile_income",
    "x5_min_pop",
    "x5_min_emp",
    "x5_min_inc",
    "x7_min_pop",
    "x7_min_emp",
    "x7_min_inc",
    "traditional_forecourt_layout",
    "rv_lanes_fueling_positions",
    "hi_flow_lanes_fueling_positions"
  )

ts_with_holidays$month_of_opening <- month(ts_with_holidays$capital_projects.soft_opening_date)
ts_with_holidays$day_of_opening <- day(ts_with_holidays$capital_projects.soft_opening_date)

# Create a function to map months to seasons
get_season <- function(month) {
  if (month %in% c(12, 1, 2)) {
    return("Winter")
  } else if (month %in% c(3, 4, 5)) {
    return("Spring")
  } else if (month %in% c(6, 7, 8)) {
    return("Summer")
  } else if (month %in% c(9, 10, 11)) {
    return("Fall")
  } else {
    return("Unknown")  # Handle unexpected values
  }
} 

# Apply the function to create the season indicator column
ts_with_holidays$season_indicator <- sapply(ts_with_holidays$month_of_opening, get_season)

df_merged <- ts_with_holidays %>%
  inner_join(qual_data, by = "site_id_msba")

df_for_modeling <- df_merged[c(1, 4:5, 7:13, 16, 17:19, 20:73)]
```

```{r}
df_for_modeling %>%
  group_by(season_indicator) %>%
  summarize(num_stores = n_distinct(site_id_msba),
            Avg_inside_sales = mean(daily_yoy_ndt.total_inside_sales),
            Avg_food_service = mean(daily_yoy_ndt.total_food_service),
            Avg_diesel_sales = mean(diesel.x),
            Avg_unleaded_sales = mean(unleaded),
            Avg_sq_ft = mean(square_feet.y),
            Avg_parking_spaces = mean(parking_spaces.x),
            Perc_with_lottery = (sum(lottery.x == "Yes")/ n()) * 100,
            Perc_with_Bonfire_Grill = (sum(bonfire_grill.x == "Yes")/ n()) * 100)
```
