---
title: "Maverik Project Exploratory Data Analysis"
author: "Jade Gosar"
output: html_document
date: "2023-10-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
library(formattable)
library(kableExtra)
```


```{r}
qualitative_data <- read_csv("qualitative_data_msba.csv")

time_series_data <- read_csv("time_series_data_msba.csv")
```

```{r}
str(qualitative_data)
str(time_series_data)

head(qualitative_data)
head(time_series_data)

summary(qualitative_data)
summary(time_series_data)
```

```{r}
is.ts(time_series_data)
```
```{r}
# Create column that shows the number of days the store has been open
ts_w_days <- time_series_data %>%
  mutate(Days_Since_Open = as.numeric(calendar.calendar_day_date - capital_projects.soft_opening_date)) %>%
  arrange(site_id_msba, calendar.calendar_day_date)

ts_w_days[c(2:4, 12:13)]
```

```{r}
# Define the major holidays data frame
major_holidays <- data.frame(
  calendar.calendar_day_date = as.Date(c(
    "2021-01-01", "2021-01-18", "2021-04-04",
    "2021-05-31", "2021-07-04", "2021-09-06", "2021-10-11",
    "2021-10-31", "2021-11-11", "2021-11-25", "2021-12-24",
    "2021-12-25", "2021-12-31", "2022-01-01", "2022-01-17",
    "2022-04-17", "2022-05-30", "2022-07-04", "2022-09-05",
    "2022-10-10", "2022-10-31", "2022-11-11", "2022-11-24",
    "2022-12-24", "2022-12-25", "2022-12-31"
  )),
  Major_Holiday = c(
    "New Year's Day", "Martin Luther King Jr. Day", "Easter Sunday",
    "Memorial Day", "Independence Day", "Labor Day", "Columbus Day",
    "Halloween", "Veterans Day", "Thanksgiving Day", "Christmas Eve",
    "Christmas Day", "New Year's Eve", "New Year's Day", "Martin Luther King Jr. Day",
    "Easter Sunday", "Memorial Day", "Independence Day", "Labor Day",
    "Columbus Day", "Halloween", "Veterans Day", "Thanksgiving Day", "Christmas Eve",
    "Christmas Day", "New Year's Eve"
  )
)
```

```{r}
# Merge the original data frame with the major holidays data frame
ts_w_holidays <- ts_w_days %>%
  left_join(major_holidays, by = c("calendar.calendar_day_date" = "calendar.calendar_day_date"))

# Make indicator for whether the day fell on a holiday given by Maverik
ts_all_holidays <- ts_w_holidays %>%
  mutate(General_Holiday = ifelse(calendar_information.holiday == "NONE", 0, 1))

# Check to make sure holidays are represented correctly
ts_all_holidays[c("calendar_information.holiday", "Major_Holiday", "General_Holiday")]

# Could remove calendar_information.holiday now that General Holiday gives same information
```

```{r}
dow_summary <- ts_all_holidays %>%
  group_by(calendar.day_of_week) %>%
  summarize(Avg_inside_sales = mean(daily_yoy_ndt.total_inside_sales),
            Avg_food_service = mean(daily_yoy_ndt.total_food_service),
            Avg_diesel_sales = mean(diesel),
            Avg_unleaded_sales = mean(unleaded))

dow_summary
```

```{r, out.width='100%', out.height='100%'}
# Define the order of days of the week
day_order <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")

# Reorder the factor levels of calendar.day_of_week
ts_all_holidays$calendar.day_of_week <- factor(ts_all_holidays$calendar.day_of_week, levels = day_order)

# Create the boxplot with the ordered days of the week
day_of_week_bp <- ggplot(ts_all_holidays,
  aes(x = calendar.day_of_week, y = unleaded, color = calendar.day_of_week)) +
  geom_boxplot(fill = "white") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  labs(title = "Unleaded Sales tend to be the highest on Fridays", x = "Day of Week", y = "Unleaded Sales") +
  guides(color = FALSE)

day_of_week_bp
```

```{r, out.width='100%', out.height='100%'}
# Reshape data from wide to long format
data_long <- dow_summary %>%
  pivot_longer(cols = starts_with("Avg_"), names_to = "Sales_Type", values_to = "Average_Sales")

# Order of the days of the week
day_order <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")

# Apply the order to the factor levels
data_long$calendar.day_of_week <- factor(data_long$calendar.day_of_week, levels = day_order)

# Create a line chart with ordered days
line_chart_ordered <- ggplot(data_long, aes(x = calendar.day_of_week, y = Average_Sales, color = Sales_Type, group = Sales_Type)) +
  geom_line(size = 2) +
  labs(title = "Trends in Sales Categories over Days of Week",
       x = "Day of the Week", y = "Average Sales", color = "Sales Type") +
  theme_minimal() +
  theme(legend.position = "top")

# Print the plot
print(line_chart_ordered)
```

```{r}
ts_all_holidays[c(1, 8:13)]

# Create the line graph
ggplot(ts_all_holidays, aes(x = Days_Since_Open, y = daily_yoy_ndt.total_inside_sales, group = site_id_msba, color = factor(site_id_msba))) +
  geom_line() +
  labs(title = "Daily YOY Total Inside Sales",
       x = "Days Since Open",
       y = "Total Inside Sales",
       color = "Store ID") +
  theme_minimal()
```

```{r, out.width='100%', out.height='100%'}
# Choose stores to highlight
selected_stores <- c(21980, 23240, 24150, 22785)

# Filter the data to include only the selected stores
stores_of_interest <- ts_all_holidays[ts_all_holidays$site_id_msba %in% selected_stores, ]

# Create the line graph
ggplot(stores_of_interest, aes(x = Days_Since_Open, y = daily_yoy_ndt.total_inside_sales, group = site_id_msba, color = factor(site_id_msba))) +
  geom_line(size = 1) +
  labs(title = "Daily Total Inside Sales for Selected Stores",
       x = "Number of Days Open",
       y = "Total Inside Sales",
       color = "Store ID") +
  theme_minimal()

# Create the line graph
ggplot(stores_of_interest, aes(x = Days_Since_Open, y = diesel, group = site_id_msba, color = factor(site_id_msba))) +
  geom_line(size = 1) +
  labs(title = "Diesel Sales in First Year for Selected Stores",
       x = "Number of Days Open",
       y = "Total Diesel Sales",
       color = "Store ID") +
  theme_minimal()

# Create the line graph of selected stores
ggplot(stores_of_interest, aes(x = Days_Since_Open, y = unleaded, group = site_id_msba, color = factor(site_id_msba))) +
  geom_line(size = 1) +
  labs(title = "Unleaded Sales in First Year for Selected Stores",
       x = "Number of Days Open",
       y = "Total Unleaded Sales",
       color = "Store ID") +
  theme_minimal()
```

## Questions:
- Should "major holiday' be defined as the ones that people are generally given the day off for? This distinguishes "all holidays" which will have noise from less significant holidays.
- Add indicator for day before and after major holidays? (Long weekends, vacation days taken around holidays, camping trips?)
- Make total sales number for each day which is all categories combined?
  - graph a breakdown of sales in percentages that are contributed by each category
- Create an indicator for what part of the season the store opened in?

- Look at differences in weekdays vs. weekend trends between the four categories
_ Facet wrap to be able to show boxplots for each category side by side?
- Density plot based on holiday not a holiday, major holiday not major holiday
